### 2020-07-02 chapters/problem-statement.tex
mais cenas

%aggregations to represent distributions
We choose to use an histogram aggregation with constant memory usage to encode the distribution of the observed values. Furthermore, we devise a sliding window approximate histogram aggregation that is maintainable in constant time in a sliding window fashion, through the use of Exponential Moving Averages (EMAs). Hence, our EMA-like histogram aggregation is ideal for the streaming scenario because of its constant time and space complexity, for every growing volumes of data.

>>>>

%aggregations to represent distributions
We choose to use an histogram aggregation with constant memory usage to encode the distribution of the observed values. Furthermore, we devise a sliding window approximate histogram aggregation that is maintainable in constant time in a sliding window fashion, through the use of Exponential Moving Averages (EMAs). Hence, our EMA-like histogram aggregation is ideal for the streaming scenario because of its constant time and space complexity, for ever growing volumes of data.
